3D Environment Generation Using Conditional Adversarial Networks

### 2019-12-11 writing/paper/paper.tex
Write more and get app running on laptop

	Both Pix2Pix and CycleGAN are conditonal networks based on the deep convolutional generative adversarial network architecture proposed by Radford et al. in 2015 \cite{radford2015unsupervised}.

	The objective function of a conditional generative adversarial networks can be expressed as:

@@

@@

@@

@@

	We use an interactive open source map tool that visualizes elevation data gathered from Mapzen's global elevation service \cite{richardson2016mapzen}.

>>>>

	The objective function of a standard conditional generative adversarial network can be expressed as:

@@

	Pix2Pix and CycleGAN both make modifications to this objective function and below we go into those changes.

@@

	This cycle consistency loss is then combined with the standard GAN loss for each GAN:

@@

	The generators then seek to minimize this objective while the discriminators try to maximize it.

	\begin{align*}
		G^*, F^* = arg \mathop{min}_{G,F} \mathop{max}_{D_x, D_y} \mathcal{L}(G, F, D_x, D_y)
	\end{align*}

@@

	We use an interactive open source map tool that visualizes elevation data gathered from Mapzen's global elevation service \cite{richardson2016mapzen}. The data for the map tool is aggrgated from 3 sources, USGS, NASA, and NGA. The map is a greyscale map, where the brightness of the pixel corresponds to the relative elevation.
